The Slowdown of TFP \\ Exogenous and Endogenous Mechanisms

### 2018-01-18 Latex/Dissertation_Workshop_23Jan2018/dw23jan2018.tex
did the counterfactual figure nicely and created the dissertation workshop presentation
… but the prezzy still needs to be reworked a lot
added acemoglu book

\documentclass{beamer}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{verbatim}
\usepackage{caption}
\usepackage{float}
\usepackage{csquotes}
\usepackage{sansmathaccent}
\usepackage{subfigure}
\usepackage{multicol}
\pdfmapfile{+sansmathaccent.map}
\def \ourFigPath {../../} 
\setbeamersize{text margin left=5mm,text margin right=12mm} 
%
\font\reali=msbm10 at 12pt
% subsets of real numbers
\newcommand{\numberset}{\mathbb}
\newcommand{\real}{\hbox{\reali R}}
\newcommand{\N}{\numberset{N}}
\newcommand{\realp}{\hbox{\reali R}_{\scriptscriptstyle +}}
\newcommand{\realpp}{\hbox{\reali R}_{\scriptscriptstyle ++}}
\newcommand{\virgolette}[1]{``#1''}
%

@@

\date{December 13, 2017}

@@

@@

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Barsky \& Sims say:}
	\label{BS_quote}

@@

\vspace{-1cm}
\noindent
\begin{figure}
\centering
\includegraphics[scale=0.3]{fig_BS_fevtable}
\end{figure}

>>>>

\documentclass{beamer}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{verbatim}
\usepackage{caption}
\usepackage{float}
\usepackage{csquotes}
\usepackage{sansmathaccent}
\usepackage{subfigure}
\usepackage{multicol}
\pdfmapfile{+sansmathaccent.map}
\def \ourFigPath {../../} 
\def \ourTablePath {../../Tables/}

\setbeamersize{text margin left=5mm,text margin right=12mm} 
%
\font\reali=msbm10 at 12pt
% subsets of real numbers
\newcommand{\numberset}{\mathbb}
\newcommand{\real}{\hbox{\reali R}}
\newcommand{\N}{\numberset{N}}
\newcommand{\realp}{\hbox{\reali R}_{\scriptscriptstyle +}}
\newcommand{\realpp}{\hbox{\reali R}_{\scriptscriptstyle ++}}
\newcommand{\virgolette}[1]{``#1''}
%

@@

\date{January 23, 2018}

@@

%%%%%  OLD STUFF
%%%%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Our starting point: Barsky \& Sims (2011)}
	\label{BS_quote}

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{What we do}

\begin{itemize}
\item We pick a particular shock out of this class of news-resembling shocks

\item We lay out a simple model of the role of this shock in explaining TFP fluctuations

\item Main analysis: Using a structural VAR, we test empirically for the contribution of this shock to TFP fluctuations against that of a classical news shock
\end{itemize}

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Theoretical model}

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Theoretical model}

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Theoretical model}

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Theoretical model}

@@

@@

\vspace{-1cm}
\noindent
\begin{figure}
\centering
\includegraphics[scale=0.3]{\ourTablePath fig_BS_fevtable}
\end{figure}
